Data Management for LSST Special Programs

### 2023-05-20 sec_intro.tex
Update sec_intro.tex

Special Programs is a Rubin Data Management (RDM) term used to refer to survey 
components with specific sky regions within or beyond the 
Wide-Fast-Deep (WFD) main survey, and/or distinct cadences or 
strategies from the WFD main survey.

There are several requirements on the Rubin Data Management System (DMS) 
related to Special Programs, summarized in Section~\ref{sec:req}.
This document recommends implementation aspects for these requirements in order to 
maximize science from Special Programs (Section~\ref{sec:sci}).

@@

Special Programs includes non-WFD LSST components such as the Deep Drilling 
Fields (DDFs) and the mini-, micro-, and nano-surveys, some of which 
might use non-standard visits with different exposure times
(Section~\ref{ssec:intro_terms}).

\subsection{Additional Terms and Definitions}\label{ssec:intro_terms}

@@

In the past the Galactic, SCP, and NES regions have been referred to as 
``mini-surveys" (see below) but this does not make them "Special Programs". 
From a survey-scheduling perspective, they are now considered part of the 
WFD survey (whether or not the scheduler software treats them as such).

>>>>

There are several requirements on the Rubin Data Management System (DMS) 
related to Special Programs, summarized in Section~\ref{sec:req}.
This document recommends implementation aspects for Rubin Data Management (RDM)
with respect to these requirements in order to 
enable science from Special Programs (Section~\ref{sec:sci}).

The three main messages of this document are:
\begin{enumerate}
\item All visits associated with a Special Program should have a region and a program label 
which is propagated to all processed images, catalog data, and alerts (Section~\ref{ssec:sci_labels}).
\item All visits that can be processed by the Prompt pipelines and generate 
alerts should be, in support of time domain and Solar System science goals (Section~\ref{ssec:proc_wfd}).
\item ``Unique and separate" data products should be generated by RDM whenever possible 
(e.g., coadded images and {\tt Object} catalogs that overlap, but are deeper or shallower than, the WFD) 
\end{enumerate}

The following sections provide greater detail and examples in support of these main messages.

\subsection{Terms and Definitions}\label{ssec:intro_terms}

\textbf{Special Programs -- } 
A Rubin Data Management (RDM) term used to refer to survey 
components with specific sky regions within or beyond the 
Wide-Fast-Deep (WFD) main survey, and/or distinct cadences or 
strategies from the WFD main survey.

@@

Special Programs includes non-WFD LSST components such as the Deep Drilling 
Fields (DDFs) and the mini-, micro-, and nano-surveys, some of which 
might use non-standard visits with different exposure times.

@@

In the past the Galactic, SCP, and NES regions have been referred to as 
``mini-surveys" (see below) but this does not make them ``Special Programs". 
From a survey-scheduling perspective, they are now considered part of the 
WFD survey (whether or not the scheduler software treats them as such).
